\hspace*{-.7em} Analysis of JavaScript Web Applications\\ Using \safe

### 2016-11-08 doc/icse-demo/main.tex

\usepackage[ruled,lined]{algorithm2e}
\usepackage{amsfonts,amssymb,amsmath, tikz,kotex,mathtools}
\usepackage{microtype,xspace}
\usepackage{url,color,multirow}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\usepackage{stmaryrd}
\newcommand{\mtt}[1]{\texttt{\small #1}}
\newcommand{\msf}[1]{{\sf\small #1}}
\newcommand{\oldsafe}{{SAFE 1.0}\xspace}
\newcommand{\safe}{{SAFE 2.0}\xspace}
\newcommand{\htmldebug}{{\sf\small HTML Debugger}\xspace}

@@

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but they are not especially
aimed for usability.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially aimed to be a playground
for advanced research in JavaScript web applications.  \safe is designed
to be light-weight, which supports configurability, extensibility, and
debuggability.
\end{abstract}

@@

To help JavaScript developers build correct programs, researchers
have developed analyzers that support various analysis techniques,
but they are not especially designed for usability.
SAFE\footnote{\url{http://plrg.kaist.ac.kr/redmine/projects/jsf/repository}}~\cite{Lee12}
is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
While more analysis techniques make SAFE more featureful,
they make the code base of SAFE large and complex, which makes it
difficult for new users to understand the code base.
TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER})
is a dataflow analysis for JavaScript that infers type information and call graphs.
It also provides analysis techniques published by the TAJS team with options;
for example, the {\tt -determinacy} option enables the techniques described in~\cite{TAJSDETER}.
WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
was originally developed for pointer analysis of Java programs, and it
also supports flow-insensitive pointer analysis of JavaScript programs.
Because WALA aims to support analysis of multiple programming languages,
the source code repository is huge with many packages.
While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
is a dynamic analysis framework for JavaScript, which provides simple
traditional dynamic analyzers like a taint analyzer as example uses of the framework.

Let us consider SAFE more closely.  It was first designed to analyze pure
JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
based on the abstract interpretation framework, and it supports
flow-sensitive and context-sensitive analyses of stand-alone JavaScript
programs.  It performs several preprocessing steps on JavaScript code to
address some quirky semantics of JavaScript such as the {\tt with}
statement~\cite{dls13}.
%, and that part has been used by other researchers~\cite{jsai,kjs}.
It was then extended to model web application execution environments
of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
and it supports analysis of interactions between JavaScript applications
and native functions in platform-specific libraries by using automatic
modeling of library functions from API specifications~\cite{SAFEWAPI}.
Recent extensions of SAFE include aggressive integration of
soundy~\cite{soundy} analysis.  Instead of analyzing the entire concrete
behaviors of programs, it supports an analysis of partial
programs by using approximate call graphs from WALA~\cite{asewala}.
It also utilizes dynamic information statically to focus on specific
environments like specific browser versions~\cite{safehybrid}.
The more advanced analysis techniques SAFE integrates,
the more difficult it is for SAFE users to understand the SAFE code base.

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in {\tt Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in {\tt Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
    // Bug detector implementation here.
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

@@

\safe has been tested using Test262, the official ECMAScript
conformance suite:
\begin{center}
\url{https://github.com/tc39/test262}
\end{center}
which helped us find and fix bugs in our modeling of builtin
functions specified in chapter 15 of the ECMAScript
specification~\cite{ECMA}.  Our regression test suite checks
whether the analysis results soundly approximate their corresponding
concrete values.  It also measures how many tests are being analyzed
precisely.  This test infrastructure with Test262 will aid \safe users
who build new analysis techniques to ``test'' the soundness of their
new analysis implementation.

>>>>

\usepackage[ruled,lined]{algorithm2e}
\usepackage{amsfonts,amssymb,amsmath, tikz,kotex,mathtools}
\usepackage{microtype,xspace}
\usepackage{url,color,multirow}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\usepackage{stmaryrd}
\newcommand{\mtt}[1]{\texttt{\small #1}}
\newcommand{\msf}[1]{{\sf\small #1}}
\newcommand{\oldsafe}{{SAFE 1.0}\xspace}
\newcommand{\safe}{{SAFE~2.0}\xspace}
\newcommand{\htmldebug}{{\sf\small HTML Debugger}\xspace}

@@

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but such analyzers are not especially
aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially designed as a playground
for advanced research in JavaScript web applications.  \safe is
light-weight, which supports configurability, extensibility, and
debuggability.
\end{abstract}

@@

To help JavaScript developers build correct programs, researchers
have developed analyzers that support various analysis techniques,
but they are not especially designed for usability.
SAFE\footnote{\url{http://plrg.kaist.ac.kr/redmine/projects/jsf/repository}}~\cite{Lee12}
is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
While more analysis techniques make SAFE more featureful,
they make the code base of SAFE large and complex, which makes it
difficult for new users to understand the code base.
TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER}
is a dataflow analysis for JavaScript that infers type information and call graphs.
It provides an analysis technique as a whole with an option instead of as
configurable components;
for example, the \mtt{-determinacy} option enables the techniques described in~\cite{TAJSDETER}.
WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
was originally developed for pointer analysis of Java programs, and it
also supports flow-insensitive pointer analysis of JavaScript programs.
Because WALA aims to support analysis of multiple programming languages,
the source code repository is huge with many packages.
While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
is a dynamic analysis framework for JavaScript, which may miss many execution flows.
It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.

Let us consider SAFE more closely.  It was first designed to analyze pure
JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
based on the abstract interpretation framework, and it supports
flow-sensitive and context-sensitive analyses of stand-alone JavaScript
programs.  It performs several preprocessing steps on JavaScript code to
address some quirky semantics of JavaScript such as the \mtt{with}
statement~\cite{dls13}.
%, and that part has been used by other researchers~\cite{jsai,kjs}.
It was then extended to model web application execution environments
of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
and it supports analysis of interactions between JavaScript applications
and native functions in platform-specific libraries by using automatic
modeling of library functions from API specifications~\cite{SAFEWAPI}.
Recent extensions of SAFE include aggressive integration of
soundy~\cite{soundy} analysis.  Instead of analyzing the entire concrete
behaviors of programs, it supports an analysis of partial
programs by using approximate call graphs from WALA~\cite{asewala}.
It also utilizes dynamic information statically to focus on specific
environments like specific browser versions~\cite{safehybrid}.
The more advanced analysis techniques SAFE integrates,
the more difficult it is for SAFE users to understand the SAFE code base.

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in \mtt{Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
    // Bug detector implementation here.
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

@@

\safe has been tested using Test262, the official ECMAScript
conformance suite:
\begin{center}
\url{https://github.com/tc39/test262}
\end{center}
which helped us find and fix bugs in our modeling of builtin
functions specified in chapter 15 of the ECMAScript
specification~\cite{ECMA}.  Our regression test suite checks
whether the analysis results soundly approximate their corresponding
concrete values.  It also measures how many tests are being analyzed
precisely.  This test infrastructure with Test262 will aid \safe users
who build new analysis techniques to ``test'' the soundness and precision of their
new analysis implementation.
